---
title: "作業1"
output: 
  html_document: 
    toc: true
    toc_depth: 1
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: false
params:
  name: ["黃鉦翔","林應廷","張又方","劉婷軒"]
  id: [710761121,710761129,710761103,710761130]
  group: "teamG"
  url: ""
---
請依狀況更改上面的name,id及group（分別代表組員姓名，學號及組號），但請勿更改下面三行的設定。  

***

姓名：`r params$name`  
學號：`r params$id`  
組號：`r params$group`  
網頁：`r params$url` 

***


```{r setup, include=FALSE}

```

```{r}

```
##1-1

$Y=Y_{-p}+{\beta}^\star P$
$=E(Y|P)= E(Y_{-p})+{\beta}^\star P|P)$
$=E[E(Y_{-p}|rincome)+\tilde{\epsilon}|P]+{\beta}^{\star}P$
$=E(2+3rincome+\tilde{\epsilon}|P)+{\beta}^{\star}P$
$=2+3E(rincome|P)+E(\tilde{\epsilon}|P)+{\beta}^{\star}P$
$=2+{\beta}^{\star}P $
其中$rincome ⊥ P$則 $E(rincome|P)=0$
$\tilde{\epsilon}⊥ P則 E(\tilde{\epsilon}|P)=0$

##1-2

##1-3

$E(Y|P)=E(Y_{-p}+\beta^*P|P)$
$=E[E(Y_{-p}|rincome)+\tilde{\epsilon}|P]+\beta^*P$
$=E(2+3rincome|P)+E(\tilde{\epsilon}|P)+\beta^*P$
$=2+3E(rincome|P)+0.5+2P+\beta^*P$
$=2+3(0.5+P)+0.5+2P+\beta^*P$
$=4+(5+\beta^*)P$ 其中$5+\beta^*$不等於$\beta^*$

$E(Y|P,rincome)=E(Y_{-p}+\beta^*P|P,rincome)$
$=E(E(Y_{-p}|rincome)+\tilde{\epsilon}|P,rincome]+\beta^*P$
$=2+3rincome+E(\tilde{\epsilon}|P,rincome)+\beta^*P$
$=2+3rincome+0.5+2P+\beta^*P$
$=2.5+3rincome+(2+\beta^*)P$ 其中$2+\beta^*$不等於$\beta^*$


##1-4

##1-5
```{r}

```

```{r}

```

```{r}

```
